\documentclass[12pt]{article}

\usepackage{xcolor} % for different colour comments

%% Comments
\newif\ifcomments\commentsfalse

\ifcomments
\newcommand{\authornote}[3]{\textcolor{#1}{[#3 ---#2]}}
\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
\else
\newcommand{\authornote}[3]{}
\newcommand{\todo}[1]{}
\fi

\newcommand{\wss}[1]{\authornote{magenta}{SS}{#1}}
\newcommand{\ag}[1]{\authornote{blue}{AG}{#1}} % Shafeeq
\newcommand{\kp}[1]{\authornote{blue}{KP}{#1}} % Keyur
\newcommand{\sr}[1]{\authornote{blue}{SR}{#1}} % Alex

\begin{document}

\title{Proof of Concept Demonstration Plan} 
\author{Alex Guerrero - guerreap\\Keyur Patel - patelk36\\Shafeeq Rabbani - rabbass}
\date{October 2, 2015}
	
\maketitle
	When building programs there are always going to be risks that will hinder the project. For the redevelopment of nibbles, a simple snake game coded in python, we must consider a handful.\par
	Python is a language all team members are familiar with but it is no one?s strongest, and no one has experience using PyGame. To overcome this, we will all familiarize ourselves with the functions used in the original code and work together as a team to redevelop the program.\par
	Language aside, another risk is applying the Model View Controller (MVC) model. Again all team members are familiar with the model, but redeveloping the code to fit this model while also modularizing the code might prove to be more difficult than anticipated. To make sure we are redeveloping the program in a timely manner, we will create a Gantt Chart to track our progress, identifying what areas might need more attention and collaboration.\par
	Unit testing will be easily done with PyUnit, but to test the graphical aspect of the game will require user testing. This is a risk because in order to do user testing you need a finished product. With the short timeline of the project it might not be possible to get user feedback and implement improvements. The Gantt chart will aid this in terms of scheduling, but another risk to the project and user testing is the fact that in order for PyGame to work you need 32-bit Python which people typically don?t have. Though it is not hard to install 32-bit Python, we know this will hinder user testing due to testers not wanting to reinstall software. Knowing this, we will get as many users as we can to play the game on our personal laptops in order to get their feedback.\par


\ag{Sample comment}
\kp{Sample comment}
\sr{Sample comment}

\end{document}

